---
title: "datawrangling"
author: "André K. Rodarte"
date: "2026-02-07"
output: html_document
---

```{r setup, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(tidytext)
library(tokenizers)
library("lexiconPT")
library(readr)
library(dplyr)
library(stringi)
library(rlang)
library(fuzzyjoin)
library(stringi)
library(tibble)
library(purrr)
library(tidyr)
library(stringr)
library(here)
```

**Set up**

```{r}
# Cleaning set up
clean_text <- function(x) {
  x %>%
    stringi::stri_trans_general(id = "Latin-ASCII") %>%
    tolower() %>%
    gsub("[[:punct:]]", "", ., perl = TRUE) %>%
    gsub("[^[:print:]]", "", ., perl = TRUE) %>%
    gsub("🄲|🯲", "", ., perl = TRUE)
}

# Formatting options
format_p_apa <- function(p) {
  dplyr::case_when(
    is.na(p)        ~ NA_character_,
    p < .001        ~ "< .001",
    p < .01         ~ paste0("= .", stringr::str_pad(round(p, 3) * 1000, 3, pad = "0")),
    p < .05         ~ paste0("= .", stringr::str_pad(round(p, 3) * 1000, 3, pad = "0")),
    TRUE            ~ paste0("= .", stringr::str_pad(round(p, 2) * 100, 2, pad = "0"))
  )
}

sig_stars <- function(p) {
  dplyr::case_when(
    is.na(p) ~ "",
    p < .001 ~ "***",
    p < .01  ~ "**",
    p < .05  ~ "*",
    TRUE     ~ ""
  )
}
```

# Format text

### FB

**Facebook posts created during the legislature, excluding the election year.**

```{r, results='hide', message=FALSE, warning=FALSE}
df_FB <- readr::read_csv(
  here::here("_unprocessed_data",
             "2024-01-06 - FB - Historical-Report-Parliamentarians-in-56th-legislature-2018-01-01---2023-01-02_with_OCR.csv"),
  show_col_types = FALSE) %>%
  dplyr::select(
    -id, -unix_timestamp, -page_category, -page_top_country,
    -page_description, -sponsor_name, -sponsor_id, -sponsor_category) %>%
  dplyr::mutate(
    timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")) %>%
  dplyr::filter(timestamp >= as.POSIXct("2019-01-01 00:00:00", tz = "UTC") &
      timestamp <= as.POSIXct("2021-12-30 23:59:59", tz = "UTC")) %>%
  dplyr::mutate(postID = dplyr::row_number())


df_FB <- df_FB %>%
  mutate(across(
    c(body, body_image, body_link, body_description, ocr_text),
    clean_text))

#Combine text
df_FB <- df_FB %>%
  mutate(
    text_combined = paste(
      coalesce(body, ""),
      coalesce(body_image, ""),
      coalesce(body_link, ""),
      coalesce(body_description, ""),
      coalesce(ocr_text, ""),
      sep = " ") %>%
      str_squish()  
  )
```

```{r}
df_FB$post_format <- dplyr::recode(df_FB$type, 
                         #Visual formats
                         "Photo" = "Image",
                         #Textual formats
                         "Link" = "Text", 
                         "Status" = "Text", 
                         #Video formats
                         "Native Video" = "Video", 
                         "Video" = "Video", 
                         "Live Video Complete" = "Video", 
                         "YouTube" = "Video", 
                         "Live Video Scheduled" = "Video", 
                         "Live Video" = "Video")

df_FB$post_format <- factor(df_FB$post_format, levels = c("Image", "Video", "Text"))

# Followers
df_FB$page_followers <- as.numeric(gsub("[^0-9]", "", df_FB$page_followers))

# Hashtags
df_FB$has_hashtags <- ifelse(is.na(df_FB$hashtags) | df_FB$hashtags == "", 0, 1)
df_FB$has_hashtags <- factor(df_FB$has_hashtags)

#ENGAGEMENT
df_FB <- df_FB %>%
  mutate(engagement = rowSums(dplyr::select(., 
    likes, likes_love, likes_wow, likes_haha, 
    likes_sad, likes_angry, likes_care, 
    comments, shares), 
    na.rm = TRUE))

# Dealing with exceptions
df_FB <- df_FB %>%
  dplyr::mutate(
    author = dplyr::if_else(
      author == "geninhozuliani.pag",
      "geninhozuliani",
      author)
  )
```

### Insta
```{r}
df_insta <- readr::read_csv(
  here::here(
    "_unprocessed_data",
    "2024-01-09 - Insta - Historical-Report-Parliamentarians-in-56th-legislature-2018-01-01---2023-01-02.csv")) %>%
  dplyr::select(-id, -thread_id, -parent_id, -thumbnail_url, -subject) %>%
    # timeframe
    dplyr::filter(timestamp >= as.POSIXct("2019-01-01 00:00:00") &
    timestamp <= as.POSIXct("2021-12-30 23:59:59")) %>%
  dplyr::mutate(
    postID = dplyr::row_number(),
    body = clean_text(body),
    # User tags
    has_hashtags = factor(ifelse(is.na(hashtags) | hashtags == "", 0, 1)),
    has_tags = factor(ifelse(is.na(usertags) | usertags == "", 0, 1)),
    # Engagement
    engagement = as.numeric(num_comments + num_likes)
  )
```

### X
 
```{r}
df_X <- readr::read_csv(
  here::here("..", "_unprocessed_data",
  "2023-03-31 - Twitter - Historical-Report-Parliamentarians-in-56th-legislature----01-jan-2018-----01--feb-2023.csv")) %>%
  # timeframe
  filter(timestamp >= as.POSIXct("2019-01-01 00:00:00") & 
         timestamp <= as.POSIXct("2021-12-30 23:59:59")) %>%
  dplyr::select(-possibly_sensitive, -language_guess, -source, -author_id, 
         -thread_id, -id, -subject, -long_lat, -place_name) %>%
  # Hashtags
  mutate(has_hashtags = ifelse(is.na(hashtags) | hashtags == "", 0, 1),
         has_hashtags = factor(has_hashtags)) %>%
  # Image
  mutate(has_image = ifelse(is.na(images) | images == "", 0, 1),
         has_image = factor(has_image)) %>%
  # Video
  mutate(has_video = ifelse(is.na(videos) | videos == "", 0, 1),
         has_video = factor(has_video)) %>%
  # User tags
  mutate(has_tags = ifelse(is.na(mentions) | mentions == "", 0, 1),
         has_tags = factor(has_tags)) %>%
  # Engagement
  mutate(engagement = retweet_count + reply_count + like_count + quote_count)

#ID
df_X$postID <- row.names(df_X)

#Clean Text
df_X$body <- clean_text(df_X$body)
```


#### Political Parties

```{r}
target_year <- 2021

# Câmara API endpoint
url_base <- "https://dadosabertos.camara.leg.br/api/v2/deputados"

# Define the date range for 2021
start_date <- paste0(target_year, "-01-01")
end_date <- paste0(target_year, "-12-31")

# Make the request 
res <- GET("https://dadosabertos.camara.leg.br/api/v2/deputados",
           query = list(
             dataInicio = "2021-01-01",
             dataFim = "2021-12-31",
             itens = 1000
           ),
           add_headers(Accept = "application/json"))

# Parse JSON and assign to a safely named object
res_data <- fromJSON(rawToChar(res$content), flatten = TRUE)

# Check column names
names(res_data$dados)

# Extract and rename relevant fields
deputados_df <- res_data$dados %>%
  dplyr::select(nome, partido = siglaPartido, uf = siglaUf) %>%
  arrange(partido, nome)

deputados_df <- deputados_df %>%
  mutate(
    name_simplified = nome %>%
      stri_trans_general("Latin-ASCII") %>%    
      str_to_lower() %>%                       
      str_replace_all(titles_to_remove, "") %>%
      str_replace_all("[0-9\\.]", "") %>%      
      str_squish()                             
  )
# write.csv(deputados_df, "deputados_df.csv", row.names = FALSE)
```



```{r}
deputados_df_handles <- read_csv("C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/_unprocessed_data/Platform_Handles.csv") 

norm_key <- function(x) {
  x %>%
    as.character() %>%
    stringi::stri_trans_general("Latin-ASCII") %>%
    str_to_lower() %>%
    str_replace("^@", "") %>%
    str_replace_all("[0-9]+", "") %>% 
    str_replace_all("[^a-z0-9]", "") %>%
    str_squish()
}
  
# Safe left join with exact match
handles_unique <- deputados_df_handles %>%
  dplyr::mutate(fb_key = norm_key(facebook_handle)) %>%
  dplyr::filter(!is.na(fb_key), fb_key != "") %>%
  dplyr::distinct(fb_key, .keep_all = TRUE) %>%
  dplyr::select(fb_key, party, state)


# Join into df_FB
df_FB <- df_FB %>%
  dplyr::mutate(fb_key = norm_key(author)) %>%
  dplyr::left_join(handles_unique, by = "fb_key")  %>%
  dplyr::select(-fb_key)
 
 #Check
 # unmatched_authors <- df_FB %>%
 #  dplyr::filter(is.na(party)) %>%
 #  dplyr::distinct(author) %>%
 #  dplyr::arrange(author)

 # Exceptions
 df_FB <- df_FB %>%
  dplyr::mutate(
    party = dplyr::case_when(
      author == "cleberverde.1010"     ~ "REPUBLICANOS",
      author == "deputadojoaocampos"   ~ "PSB",
      author == "joaobacelaroficial"   ~ "PL",
      TRUE ~ party
    ),
    state = dplyr::case_when(
      author == "cleberverde.1010"     ~ "MA",
      author == "deputadojoaocampos"   ~ "PE",
      author == "joaobacelaroficial"   ~ "BA",
      TRUE ~ state
    )
  )
```

##### Parties' Ideology
```{r}
# List of parties and their respective ideological score
parties <- read_csv("C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/_unprocessed_data/parties.csv")

df_FB <- df_FB %>%
  mutate(party = str_to_upper(party))   

parties <- parties %>%
  mutate(Party = str_to_upper(Party))

# Join ideological score
df_FB <- df_FB %>%
  left_join(
    parties %>% dplyr::select(Party, `2021_ideological_score`),
    by = c("party" = "Party")
  )
```

Note: I added the same ideological score as SOLIDARIEDADE to PROS considering: <https://www.tse.jus.br/comunicacao/noticias/2023/Fevereiro/partido-republicano-da-ordem-social-pros-e-incorporado-ao-solidariedade>. By the same criterium, I gave the same ideological score to PTB and PATRIOTA: <https://www.cnnbrasil.com.br/politica/tse-aprova-fusao-de-ptb-e-patriota-e-novo-partido-tera-direito-a-r-228-mi/>.


##### Incumbency
```{r}
parties  <- readr::read_csv2(here::here("..", "_processed_data", "parties_ideology_gov.csv"))

#Accounting for party merges and name changes
df_FB <- df_FB %>%
  mutate(party = str_to_upper(party),
         party = dplyr::recode(party, "PODEMOS" = "PODE", "PRB" = "REPUBLICANOS"))
  #Update ideology_score
  df_FB <- df_FB %>%
    left_join(
    parties %>% dplyr::select(Party, ideology_party = `2021_ideological_score`),
    by = c("party" = "Party")
  ) %>%
  # Use the actual column name from your dataframe here
  mutate(ideology_2021 = coalesce(`2021_ideological_score`, ideology_party)) %>% 
  dplyr::select(-ideology_party)
  #Sanity check
  # na_by_party <- df_FB %>%
  # filter(is.na(ideology_2021)) %>%
  # count(party, sort = TRUE)
```


# Cross Platform
```{r}
handles_cross_plat <- read_csv("C:/Users/andre/OneDrive/UT Austin/Dissertation [PhD UT]/Dissertation Articles/Lacracao Logic/56_Legislature_Cross_platform_handles.csv")

clean_handle <- function(x) {
  x %>%
    as.character() %>%
    stringi::stri_trans_general("Latin-ASCII") %>%
    stringr::str_to_lower() %>%
    stringr::str_replace("^@", "") %>%
    stringr::str_replace_all("https?://", "") %>%
    stringr::str_replace_all("www\\.", "") %>%
    stringr::str_replace_all("[0-9\\.]", "") %>%   
    str_replace_all("[^a-z]", "") %>%     
    stringr::str_squish()
}

# For deputies who changed their account names (e.g. Joao Campos)
alias_handle <- function(x) {
  x <- as.character(x)
  z <- str_to_lower(x)
  z <- if_else(z == "deputadojoaocampos", "joaocampos", z)
  z <- if_else(z %in% c("geninhozuliani.pag", "geninhozuliani_pagina", "geninhozulianipag"),
               "geninhozuliani", z)
  z <- str_replace(z, "^_+", "") # remove leftover leading underscores 
  z
}
```

**Identify X/IG only Handles**
```{r}
df_insta <- df_insta %>%
  mutate(author = alias_handle(author))
df_X <- df_X %>%
  mutate(author = alias_handle(author))

# Bridge source table
handles_cross_plat <- handles_cross_plat %>%
  mutate(
    `instagram handle` = alias_handle(`instagram handle`),
    `twitter handle`   = alias_handle(`twitter handle`),
    `facebook handle`  = alias_handle(`facebook handle`)
  )
```

```{r}
fb_truth <- df_FB %>%
  transmute(
    fb_key = clean_handle(author),
    party  = str_to_upper(party),
    state,
    ideology_2021
  ) %>%
  mutate(party = dplyr::recode(party,
      "PODEMOS" = "PODE",
      "PRB"     = "REPUBLICANOS")
  ) %>%
  distinct(fb_key, .keep_all = TRUE) %>%
  left_join(
    parties %>%
      transmute(party = Party, ProGov, ideology_party = `2021_ideological_score`), by = "party"
  ) %>%
  mutate(ideology_2021 = coalesce(ideology_2021, ideology_party)) %>%
  dplyr::select(-ideology_party)
```

**Insta Only**
```{r}
ig_lookup <- handles_cross_plat %>%
  transmute(
    ig_key = clean_handle(alias_handle(`instagram handle`)),
    fb_key = clean_handle(alias_handle(`facebook handle`)),
    party_from_handles = str_to_upper(partido),
    ideology_from_handles = `2021_ideological_score`,
    state_from_handles = state
  ) %>%
  filter(!is.na(ig_key), ig_key != "") %>%
  distinct()
ig_lookup <- ig_lookup %>%
  mutate(
    party_from_handles = dplyr::recode(party_from_handles,
      "PODEMOS" = "PODE",
      "PRB"     = "REPUBLICANOS"
    )
  )
```

**Twitter Only**
```{r}
tw_lookup <- handles_cross_plat %>%
  transmute(
    tw_key = clean_handle(alias_handle(`twitter handle`)),
    fb_key = clean_handle(alias_handle(`facebook handle`)),
    party_from_handles    = str_to_upper(partido),
    ideology_from_handles = `2021_ideological_score`,
    state_from_handles    = state
  ) %>%
  filter(!is.na(tw_key), tw_key != "") %>%
  distinct()
# Harmonize party aliases 
tw_lookup <- tw_lookup %>%
  mutate(
    party_from_handles = dplyr::recode(party_from_handles,
      "PODEMOS" = "PODE",
      "PRB"     = "REPUBLICANOS"
    )
  )

tw_lookup_1to1 <- tw_lookup %>%
  # mark which rows have an fb_key that is in fb_truth
  mutate(
    fb_in_truth = !is.na(fb_key) & fb_key %in% fb_truth$fb_key,
    has_party   = !is.na(party_from_handles) & party_from_handles != ""
  ) %>%
  arrange(
    tw_key,
    desc(fb_in_truth),   
    desc(!is.na(fb_key) & fb_key != ""),
    desc(has_party)
  ) %>%
  group_by(tw_key) %>%
  slice(1) %>%         
  ungroup() %>%
  dplyr::select(-fb_in_truth, -has_party)

# sanity check: now unique
stopifnot(!anyDuplicated(tw_lookup_1to1$tw_key))
```


```{r}
# df_X <- df_X %>%
#   dplyr::select(
#     -any_of(c("partido", "party")),
#     -matches("^ideology_2021(\\..+)?$"),
#     -matches("^ProGov(\\..+)?$"),
#     -matches("^state(\\..+)?$")
#   )

df_insta <- df_insta %>%
  mutate(ig_key = clean_handle(alias_handle(author))) %>%
  left_join(ig_lookup, by = "ig_key", relationship = "many-to-one") %>%
  left_join(fb_truth,  by = "fb_key", relationship = "many-to-one") %>%
  mutate(
    party         = coalesce(party, party_from_handles),
    ideology_2021  = coalesce(ideology_2021, ideology_from_handles),
    state         = coalesce(state, state_from_handles)
  ) %>%
  # bring ProGov only as a fallback, then coalesce
  left_join(
    parties %>% transmute(party = Party, ProGov_fallback = ProGov),
    by = "party",
    relationship = "many-to-one"
  ) %>%
  mutate(ProGov = coalesce(ProGov, ProGov_fallback)) %>%
  dplyr::select(-ig_key, -fb_key,-party_from_handles, -ideology_from_handles, -state_from_handles,-ProGov_fallback)
  #Inspect missing cases
  insta_missing_party <- df_insta %>%
  filter(is.na(party)) %>%
  distinct(author) %>%
  arrange(author)
  # insta_missing_party

############# TWITTER ##################
df_X <- df_X %>%
  mutate(tw_key = clean_handle(alias_handle(author))) %>%
  left_join(tw_lookup_1to1, by = "tw_key", relationship = "many-to-one") %>%
  left_join(fb_truth,       by = "fb_key", relationship = "many-to-one") %>%
  mutate(
    party         = coalesce(party, party_from_handles),
    ideology_2021  = coalesce(ideology_2021, ideology_from_handles),
    state         = coalesce(state, state_from_handles)
  ) %>%
  left_join(
    parties %>% transmute(party = Party, ProGov_fallback = ProGov),
    by = "party",
    relationship = "many-to-one"
  ) %>%
  mutate(ProGov = coalesce(ProGov, ProGov_fallback)) %>%
  dplyr::select(-tw_key, -fb_key, -party_from_handles, -ideology_from_handles, -state_from_handles,-ProGov_fallback)
  #Inspect for missing cases
  X_missing_party <- df_X %>%
  filter(is.na(party)) %>%
  distinct(author) %>%
  arrange(author)
  # X_missing_party
```
# Clean 
```{r}
df_fb_clean <- df_FB %>%
  dplyr::rename(ideology_2021 = `2021_ideological_score`)

df_fb_clean <- df_fb_clean %>%
  dplyr::select(postID, 
                author,
                page_name,
                thread_id,
                text_combined,
                timestamp,
                page_created,
                page_likes,
                page_id,
                page_followers,
                type,
                post_format,
                has_hashtags,
                engagement,
                interactions,
                comments,
                shares,        
                likes, 
                likes_love,  
                likes_wow,   
                likes_haha,   
                likes_sad,   
                likes_angry,
                likes_care,
                views_post,
                views_total,
                views_total_crossposts,
                hashtags,
                url,
                url_original,
                party,
                state,
                ideology_2021,
                ProGov)


df_insta_clean <- df_insta %>% 
  dplyr::select(postID,
                author, 
                body,
                timestamp,
                type,
                url,
                hashtags,
                usertags,
                num_likes,
                num_comments,
                engagement,
                has_hashtags,
                has_tags,
                party,
                ideology_2021,
                ProGov)
                
df_X_clean <- df_X %>% 
  dplyr::select(
    postID,
    author,
    author_fullname,
    author_followers,
    body,
    timestamp,
    unix_timestamp,
    link,
    urls,
    is_retweet,
    retweeted_user,
    is_quote_tweet,
    quoted_user,
    is_reply,
    replied_user,
    retweet_count,
    hashtags,
    images,
    videos,
    mentions,
    has_hashtags,
    has_image,
    has_video,
    has_tags,
    like_count,
    quote_count,
    reply_count,
    impression_count,
    engagement,
    party,
    ideology_2021,
    ProGov)
```

# Robustness Checks
```{r}
# Helper to build one formatted correlation table
make_corr_table <- function(df, vars) {
  
  # Keep only requested variables that actually exist in the data
  vars <- vars[vars %in% names(df)]
  
  # Function to compute one cell
  get_corr_cell <- function(v1, v2, data) {
    x <- data[[v1]]
    y <- data[[v2]]
    
    # Pairwise complete cases
    ok <- stats::complete.cases(x, y)
    x <- x[ok]
    y <- y[ok]
    
    # Avoid errors when there is no variation / too few cases
    if (length(x) < 3 || length(unique(x)) < 2 || length(unique(y)) < 2) {
      return(NA_character_)
    }
    
    test <- suppressWarnings(stats::cor.test(x, y, method = "pearson"))
    r <- unname(test$estimate)
    p <- test$p.value
    
    paste0(
      sprintf("%.3f", r),
      sig_stars(p),
      "\n(",
      format_p_apa(p),
      ")"
    )
  }
  
  # Build matrix
  out <- expand_grid(row_var = vars, col_var = vars) %>%
    mutate(
      value = map2_chr(row_var, col_var, ~{
        if (.x == .y) {
          "1.000\n(—)"
        } else {
          get_corr_cell(.x, .y, df)
        }
      })
    ) %>%
    pivot_wider(names_from = col_var, values_from = value) %>%
    rename(Variable = row_var)
  
  out
}

# Facebook
fb_vars <- c("comments", "shares", "likes", "likes_love", "likes_wow",
  "likes_haha", "likes_sad", "likes_angry", "likes_care")
fb_corr_table <- make_corr_table(df_FB, fb_vars)

# Instagram
insta_vars <- c("num_comments", "num_likes")

insta_corr_table <- make_corr_table(df_insta, insta_vars)

# Twitter
twitter_vars <- c("retweet_count", "reply_count", "like_count", "quote_count")

twitter_corr_table <- make_corr_table(df_X, twitter_vars)

# View
fb_corr_table
insta_corr_table
twitter_corr_table

# Export
openxlsx::write.xlsx(
  list(
    Facebook = fb_corr_table,
    Instagram = insta_corr_table,
    Twitter = twitter_corr_table
  ),
  file = here::here("..", "_output", "engagement_component_correlations.xlsx"),
  overwrite = TRUE
)
```





# Export
```{r}
# Data on deputados
readr::write_csv2(
  deputados_df,
  here::here("_processed_data", "deputados_df.csv"))
readr::write_rds(
  deputados_df,
  here::here("_processed_data", "deputados_df.rds"))
readr::write_csv2(
  deputados_df_handles,
  here::here("_processed_data", "deputados_df_handles.csv"))
readr::write_rds(
  deputados_df_handles,
  here::here("_processed_data", "deputados_df_handles.rds"))

# Platform data
readr::write_csv2(
  df_fb_clean,
  here::here("..", "_processed_data", "df_fb_clean.csv")
  )
readr::write_rds(
  df_fb_clean,
  here::here("..", "_processed_data", "df_fb_clean.rds")
  )

readr::write_csv2(
  df_insta_clean,
  here::here("..", "_processed_data", "df_insta_clean.csv"))
readr::write_rds(
  df_insta_clean,
  here::here("..", "_processed_data", "df_insta_clean.rds"))

readr::write_csv2(
  df_X_clean,
  here::here("..", "_processed_data", "df_X_clean.csv"))
readr::write_rds(
  df_X_clean,
  here::here("..", "_processed_data", "df_X_clean.rds"))
```
